\section{Future Work}


        \begin{quote}
        \vspace{2mm}
            \textit{``\acl{app} can be someone to talk to\ldots I don't know if you have seen the movie, `Her'~\cite{spike2014her}. Something like that. The `Her' thing is not to automate your life or to remind you anything. Google Assistant can do that. Someone to talk with, not to get any feedback, just to review your day\ldots''} [P16]
        \vspace{2mm}
        \end{quote} 
    
        Looking forward, as speech-enabled devices become more mainstream, it is worth considering the futures we desire, and how we might design to sustainably support them. What role do we want these devices to play in our lives? 
        
        Although many participants expressed hesitation in considering health recommendations provided by a \ac{CA}, several mentioned that they would welcome non-intrusive recommendations that reminded them of the things they could do, although added that a \ac{CA} should grant them broad scope to develop and make their own decisions; \textit{``You can remind sometimes. Like `Do you want to do a breathing exercise to improve your mental health?' and then you can say `Yes' or `No'. I think it's important that you still have the possibility to say no''} [P14]. Other participants suggested incorporating humor and health advice into conversations with \acl{app}.
        
        These possibilities raise additional questions. Do we, for example, 
            want agents to provide recommendations for our health and wellbeing, or 
            prove truly capable of holding rich conversations, or 
            might we prefer uncaring machines, who may also ironically be best placed to provide an experience of care?
        These are the kinds of questions raised by this study, as one of the first to engage such a participant group in the real-world use of \ac{CA} technologies, and we hope will serve to fuel future research efforts, as we continue to reflect on the implications of growing adoption of these technologies.
    
    
    
    